Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-07-11 paper/main.tex
removing redundant plots

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
\caption{Interweb alignment for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
\caption{Interweb alignment for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/Web.ps}
\caption{Median of the interweb alignment for the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
\caption{Shape alignment for the vweb at $256^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
\caption{Shape alignment for the tweb at $256^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
\caption{Shape alignment for the vweb at $512^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
\caption{Shape alignment for the tweb at $512^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/VWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/TWeb.ps}
\caption{Median of the shape alignment for the two web  and the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
\caption{Median of the angular momentum for the two web  and the two grid resolution.}
\end{figure*}

@@

>>>>

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
%\caption{Interweb alignment for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
%\caption{Interweb alignment for $512^3$ grid resolution.}
%\end{figure*}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../plot2/Mass/Web.ps}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
%\caption{Shape alignment for the vweb at $256^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
%\caption{Shape alignment for the tweb at $256^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
%\caption{Shape alignment for the vweb at $512^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
%\caption{Shape alignment for the tweb at $512^3$ resolution.}
%\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
%\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
%\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
%\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
%\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
%\end{figure*}

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the peculiar
  velocity of each halo.} 
\end{figure*}
